---
title: "オープンソフトウェアRによる再現可能な数理モデル解析－水田水中除草剤動態を例に－" 
subtitle: "2. ハンズオン"
author: "近藤 圭"
author-meta: "一般財団法人残留農薬研究所 化学部"
date: '`r format(Sys.time(), "%Y/%m/%d %H:%M")`'
output:
  html_document
  pdf_document
---

```{r, include = FALSE}
# read R libraries
library(FME)
library(hydroGOF)
library(sensitivity)
library(readr)
library(ggplot2)

# Read PCPF-1R model and sub-function
source("R/PCPF-1R.R")
source("R/PPCPF.R")
source("R/PCONC.R")
```

# (1) 解析準備～データの前処理

`data-raw`フォルダ内の以下のファイルに，実験データを生データとして入力する。

-   水中残留濃度 (*data_conc_label_1.csv*)

-   水収支 (*data_wb_1.csv*)

-   実験圃場の情報 (*input_experiment.csv*)

-   処理農薬製剤情報 (*input_pesticide_label_1.csv*)

対象農薬中有効成分の対象成分の分子量，水溶解度，蒸気圧，土壌吸着性および分解情報を以下のファイルに入力する。

-   物理的化学的パラメータ (*input_pesticide_physchem.csv*)

本稿では原則として，全てが一括で入手可能である農薬抄録あるいは農薬の審査報告書からの取得を推奨する。 これらを用いて表-1に示すPCPF-1Rモデルの入力パラメータセットを前処理済みデータとして作成する。

```{r }
# Read raw data
input_EXP       <-  read_csv("data-raw/input_experiment.csv")
input_PHYSCHEM  <-  read_csv("data-raw/input_pesticide_physchem.csv")
input_LAB       <-  read_csv("data-raw/input_pesticide_label_1.csv")
data_conc       <-  read_csv("data-raw/data_conc_label_1.csv")

# Create parameter set
input_param     <-  PPCPF(input_EXP, input_PHYSCHEM, input_LAB)

# Cleaning concentration data for model calibration
data_Cpw        <-  PCONC(data_conc)

# Save pre-processed data
save(input_param, 
     file = "data/input_param_label_1_cold.RData")
write.csv(input_param, "data/input_label_1_cold.csv", 
          quote=FALSE, row.names=FALSE)
save(data_Cpw, 
     file = "data/data_conc_label_1.RData")
write.csv(data_Cpw, "data-raw/P_data_conc_label_1.csv", 
          quote=FALSE, row.names=FALSE)

```

```{r }
# STEP 1: Run cold simulation with uncalibrated parameters
```

```{r }

# Read input data  
load("data/input_param_label_1_cold.RData")
p     <-  input_param
  
# Read observation data
load("data/data_conc_label_1.RData")
d     <-  data_Cpw
er    <-  max(d[,2])*sqrt(length(d[,2]))
d$W   <-  d[,2]#er
obs   <-  read.csv("data-raw/data_conc_label_1.csv",header=T)  # For visual presentation 

# Read water balance data:  
water <-  read.csv("data-raw/data_wb_1.csv",header=T)

# Run cold simulation
out1  <-  PCPF1R(p, p, water=water, DMAX=21, fdes=1, type=2)
save(out1, file = "output/01_coldrun_output.RData")
write.csv(out1, "output/01_coldrun_output.csv", quote=FALSE, row.names=FALSE)

# Goodness of fitting for cold simulation
Y      <-  d[1]
Z1     <-  c("Time","Cpw")
out1d  <-  XXL(out1, Y, Z1)
stat_1 <-  gof(sim=out1d$Cpw, obs=d$Cpw)
stat_1
save(stat_1, file = "output/01_coldrun_stat.RData")

# Visual checks for both linear and log scales
png("figs/01_coldrun_conc_linear.png", 
    width = 6, height = 6, units = 'in', res = 300)
  plot(out1$Time, out1$Cpw, xlim=c(0,21), ylim=c(0,1), lty=1,lwd = 2, type="l",
       main=paste(p$name,": Cold simulation at ",p$plot), ylab ="Concentration (mg/L)", 
       xlab = "Day after application (day)",cex.lab=1.2)
  for (i in 1:(nrow(obs))) {
    if (obs[i,2]=="="){
      points(obs$DAHA[i], obs$CONC.[i], pch=1, cex=2.5, col = "red")
    } else if(obs[i,2]=="<") {
      points(obs$DAHA[i], obs$CONC.[i], pch=19, cex=2.5, col = "red")
    }
  }
  legend("topright", c("measured", "simulated"),lty = c(NA, 1), 
         pch = c(1, NA), cex=1.2,bty="n", col=c("red", "black"))
dev.off()

png("figs/01_coldrun_conc_log.png", 
    width = 6, height = 6, units = 'in', res = 300)
  plot(0,0.001, type = "n", bty = "n", xlim=c(0,21), ylim=c(0.001,1),
       yaxt="n", xaxt = "n", ylab = "Concentration (mg/L)", 
       xlab="Day after application (day)",log="y",cex.lab=1.2,
       main=paste(p$name,": Cold simulation at ",p$plot))
  axis(1, at=seq(0,21,3),cex.axis=1.1)
  axis(2, at=c(0.001, 0.01 ,0.1,1), 
       labels=c("0.001","0.01", "0.1","1"),las=1, cex.axis=1.2)
  at.y <- outer(1:9, 10^(-3:0))
  lab.y <- ifelse(log10(at.y) %% 1 == 0, at.y, NA)
  axis(2, at=at.y, labels=lab.y, tcl=par("tcl")*0.5, las=1, cex.axis=1.2)
  lines(out1$Time, out1$Cpw, lty=1,lwd = 2)
  box()
  for (i in 1:(nrow(obs))) {
    if (obs[i,2]=="="){
      points(obs$DAHA[i], obs$CONC.[i], pch=1, cex=2.5, col = "red")
    } else if(obs[i,2]=="<") {
      points(obs$DAHA[i], obs$CONC.[i], pch=19, cex=2.5, col = "red")
    }
  }
  legend("topright", c("measured", "simulated"),lty = c(NA, 1), 
         pch = c(1, NA), cex=1.2,bty="n", col=c("red", "black"))
dev.off()

```

```{r }
# STEP 2: Grobal sensitivity
```

```{r }
# Select varied parameters
# For granule include "kdiss" in p1
# For flowable/emulsion include "alp" in p1
p1   <- p[c("alp","Kd","ksorp","f","kvol","kdiff","kbulk","kbios")]
p2   <- p[-which(names(p) %in% names(p1))] 

# Define parameter range
# For Kd, set upper and lower bounds as those of experimental results
# For ksorp, apply 100-folds range
# For f, set 0.1-1 as default
# For other parameters, set upper and lower bounds as X*M and 1/X*M where M is parameter value
parRanges <- data.frame(min=c(0.5*as.numeric(p1["alp"]),
                              10,
                              0.2*as.numeric(p1["ksorp"]),
                              0.1,
                              0.5*as.numeric(p1["kvol"]),
                              0.5*as.numeric(p1["kdiff"]),
                              0.05*as.numeric(p1["kbulk"]),
                              0.5*as.numeric(p1["kbios"])
                              ),
                        max=c(2*as.numeric(p1["alp"]),
                              100,
                              5*as.numeric(p1["ksorp"]),
                              1,
                              2*as.numeric(p1["kvol"]),
                              2*as.numeric(p1["kdiff"]),
                              20*as.numeric(p1["kbulk"]),
                              2*as.numeric(p1["kbios"])
                              )
                        )
rownames(parRanges) <- c("alp","Kd","ksorp", "f","kvol","kdiff","kbulk","kbios") 

# Define sensitivity function
crlF <- function (par){
        out <- XX(PCPF1R(par, parms2 = p2, water=water,
                  DMAX=21,fdes=1,type=2)
                  )
        ssr <- modCost(mod=out,obs=d, x="Time", err="W")$model
        return(ssr)
        }

# Run Monte-Carlo Simulation (MCS) with latin-hypercube sampling for SRRC calculation
print(system.time(
      CRL1 <- modCRL(func=crlF, parms=p, dist="latin", parRange=parRanges, num=250)
      ))
save(CRL1, file="output/02_sensitivity_MCS_1.RData")
write.csv(CRL1, "output/02_sensitivity_MCS_1.csv", quote=FALSE, row.names=FALSE)

# Visual check
png("figs/02_sensitivity_MCS_1.png", 
    width = 8, height = 6, units = 'in', res = 300)
  plot(CRL1, ylab="ModelCost", trace=TRUE, main="",cex.lab=1.5,cex.axis=1.3)
dev.off()
  
# Estimate SRRC
X    <- CRL1[,1:8]
y    <- as.vector(CRL1[,9])
SRRC <- src(X, y, rank = TRUE)
print(SRRC)
save(SRRC, file="output/02_sensitivity_SRRC.RData")
SRRC_table <- data.frame(parameter=row.names(SRRC$SRRC),SRRC$SRRC)
write.csv(SRRC_table, 
          file = "tables/02_sensitivity_SRRC.csv", 
          row.names = FALSE)
png("figs/02_sensitivity_SRRC.png", 
    width = 8, height = 6, units = 'in', res = 300)
  plot(SRRC)
  abline(h=0,col="red")
dev.off()

# Select highly sensitive parameters (e.g., SRRC > 0.01) among p1
p3   <- p[SRRC_table$parameter[abs(SRRC_table$original)>0.01]]
p4   <- p[-which(names(p) %in% names(p3))] 

# Reduce target parameters for visual assessment of prior parameter uncertainty
parRanges2 <- parRanges[names(p3),] 

# Run MCS with latin-hypercube sampling for visual assessment of prior parameter uncertainty
SF <- function (pars) {
   out <- PCPF1R(pars,parms2=p4,water=water,DMAX=21,fdes=1,type=2)
   return(out)
   }
print(system.time(
      Sens1 <-sensRange(func=SF, parms=p3, dist="latin", sensvar="Cpw", parRange=parRanges2, num=250)
      ))
save(Sens1, file="output/02_sensitivity_MCS_2.RData")
write.csv(Sens1, "output/02_sensitivity_MCS_2.csv", quote=FALSE, row.names=FALSE)

# Visual check
# Check if observed data (>LOQ) are within the range of prediction range
# If not, reset parameter range of "parRanges2" and rerun 
png("figs/02_sensitivity_MCS_2_linear.png", 
    width = 6, height = 6, units = 'in', res = 300)
  plot(summary(Sens1), xlim=c(0,21), ylim=c(0, 1), ylab = "Concentration (mg/L)", quant=TRUE,
       main=paste(p$name,": Grobal sensitivity at ",p$plot), xlab="Day after application",
       cex.lab=1.2, legpos="topright")
  for (i in 1:(nrow(obs))) {
    if (obs[i,2]=="="){
      points(obs$DAHA[i], obs$CONC.[i], pch=1, cex=2.5, col = "red")
    } else if(obs[i,2]=="<") {
      points(obs$DAHA[i], obs$CONC.[i], pch=19, cex=2.5, col = "red")
    }
  }
dev.off()

png("figs/02_sensitivity_MCS_2_log.png", 
    width = 6, height = 6, units = 'in', res = 300)
  plot(summary(Sens1), xlim=c(0,21), ylim=c(0.001, 1), ylab = "Concentration (mg/L)", quant=TRUE,
       main=paste(p$name,": Grobal sensitivity at ",p$plot), xlab = "Day after application",cex.lab=1.2,
       legpos="topright", log="y")
  for (i in 1:(nrow(obs))) {
    if (obs[i,2]=="="){
      points(obs$DAHA[i], obs$CONC.[i], pch=1, cex=2.5, col = "red")
    } else if(obs[i,2]=="<") {
      points(obs$DAHA[i], obs$CONC.[i], pch=19, cex=2.5, col = "red")
    }
  }
dev.off()

```

```{r }
# STEP 3: Local sensitivity analysis
```

```{r }

# define new function
SF <- function (par) {
  out <- PCPF1R(par, parms2 = p4, water=water,DMAX=21,type=2, fdes=1)
  return(modCost(mod = out, obs = d, x= "Time", err="W"))
  }
SFA <- sensFun(func = SF, parms = p3)
save(SFA, file="output/03_sensitivity_SFA.RData")

png("figs/03_sensitivity_local.png", 
    width = 6, height = 6, units = 'in', res = 300)
  plot(SFA,legpos="bottomright")
dev.off()

# Summary of local sensitivity analysis
summary(SFA)
write.csv(summary(SFA), 
          file = "tables/03_sensitivity_local.csv", 
          row.names = TRUE)

# Parameter identifiability
# select "identifiable (collinearity < 20)" sets
ident         <- collin(SFA, which = "Cpw")
save(ident, file="output/03_sensitivity_ident.RData")
calibpar_list <- ident[ident[,"collinearity"] < 20,]
write.csv(calibpar_list, 
          file = "tables/03_sensitivity_ident.csv", 
          row.names = TRUE)
calibpar_list

```

```{r }
# STEP 4: Model fitting
```

```{r }

# Select parameter set for calibration
# Set row number of calibpar_list in instead of "17"
calibpar <-  colnames(calibpar_list[17,which(calibpar_list[17,]==1)])
p5       <-  p[calibpar]
p6       <-  p[-which(names(p) %in% names(p5))] 
            
F <- function (par) {
  out <- PCPF1R(exp(par), parms2 = p6, water=water,DMAX=21,type=2, fdes=1)
  return(modCost(mod = out, obs = d, x= "Time", err="W"))
  }

# Set initial parameter set and parameter range
ppl <- as.numeric(parRanges2[names(p5),1])
ppu <- as.numeric(parRanges2[names(p5),2])

# log-transformation
pp  <- log(unlist(p5))
ppl <- log(ppl)
ppu <- log(ppu)

# Start fitting
print(system.time(Fit <- modFit(p=pp,f=F,lower=ppl,upper=ppu,method="Pseudo",
                                control=c(numiter=1000,varleft=0.01,verbose=TRUE)
                                )
                  )
      )


# Check results
summary(Fit)
exp(coef(Fit))
save(Fit, file="output/04_fitting_Fit.RData")

# Save calibrated parameter set
input_param_2  <- p
for (j in 1:length(exp(coef(Fit)))){
  nval = names(exp(coef(Fit)[i]))
  input_param_2[nval] = as.numeric(exp(coef(Fit)[i]))
}
save(input_param_2, file = "data/input_param_label_1_calib.RData")
write.csv(input_param_2, "data/input_label_1_calib.csv", 
          quote=FALSE, row.names=FALSE)

# Run calibrated simulation
out2 <- PCPF1R(exp(coef(Fit)), parms2 = p6, water=water,DMAX=21,type=2,fdes=1)
save(out2, file = "output/04_fitting_output.RData")
write.csv(out2, "output/04_fitting_output.csv", quote=FALSE, row.names=FALSE)

# Goodness of fitting for cold simulation
Y      <-  d[1]
Z1     <-  c("Time","Cpw")
out2d  <-  XXL(out2, Y, Z1)
stat_2 <-  gof(sim=out2d$Cpw, obs=d$Cpw)
stat_2
save(stat_2, file = "output/04_fitting_stat.RData")

# Visual checks for both linear and log scales
png("figs/04_fitting_conc_linear.png", 
    width = 6, height = 6, units = 'in', res = 300)
  plot(out2$Time, out2$Cpw, xlim=c(0,21), ylim=c(0,1), lty=1,lwd = 2, type="l",
       main=paste(p$name,": Calibrated simulation at ",p$plot), ylab ="Concentration (mg/L)", 
       xlab = "Day after application (day)",cex.lab=1.2)
  for (i in 1:(nrow(obs))) {
    if (obs[i,2]=="="){
      points(obs$DAHA[i], obs$CONC.[i], pch=1, cex=2.5, col = "red")
    } else if(obs[i,2]=="<") {
      points(obs$DAHA[i], obs$CONC.[i], pch=19, cex=2.5, col = "red")
    }
  }
  legend("topright", c("measured", "simulated"),lty = c(NA, 1), 
         pch = c(1, NA), cex=1.2,bty="n", col=c("red", "black"))
dev.off()

png("figs/04_fitting_conc_log.png", 
      width = 6, height = 6, units = 'in', res = 300)
  plot(0,0.001, type = "n", bty = "n", xlim=c(0,21), ylim=c(0.001,1),
       yaxt="n", xaxt = "n", ylab = "Concentration (mg/L)", 
       xlab="Day after application (day)",log="y",cex.lab=1.2,
       main=paste(p$name,": Calibrated simulation at ",p$plot))
  axis(1, at=seq(0,21,3),cex.axis=1.1)
  axis(2, at=c(0.001, 0.01 ,0.1,1), 
       labels=c("0.001","0.01", "0.1","1"),las=1, cex.axis=1.2)
  at.y <- outer(1:9, 10^(-3:0))
  lab.y <- ifelse(log10(at.y) %% 1 == 0, at.y, NA)
  axis(2, at=at.y, labels=lab.y, tcl=par("tcl")*0.5, las=1, cex.axis=1.2)
  lines(out2$Time, out2$Cpw, lty=1,lwd = 2)
  box()
  for (i in 1:(nrow(obs))) {
    if (obs[i,2]=="="){
      points(obs$DAHA[i], obs$CONC.[i], pch=1, cex=2.5, col = "red")
    } else if(obs[i,2]=="<") {
      points(obs$DAHA[i], obs$CONC.[i], pch=19, cex=2.5, col = "red")
    }
  }
  legend("topright", c("measured", "simulated"),lty = c(NA, 1), 
         pch = c(1, NA), cex=1.2,bty="n", col=c("red", "black"))
dev.off()

```

```{r }
# STEP 5: Assessing parameter uncertainty using MCMC
```

```{r }

# Set MCMC inputs
var0 <- Fit$var_ms_unweighted
cov0 <- summary(Fit)$cov.scaled*2.4^2/5
#cov0 <- diag(0.001,3)

F2 <- function (par) {
   out <- PCPF1R(exp(par), parms2 = p6, water=water,DMAX=21,type=2, fdes=1)
   Y         <-  d[1]
   Z1        <-  c("Time","Cpw")
   outd      <-  XXL(out, Y, Z1)
   residuals <-  (outd$Cpw-d$Cpw)/d$W
   return(sum(residuals^2))
}

print(system.time(
      MCMC <- modMCMC(f=F2, p=Fit$par, niter=6000, upper=ppu, lower=ppl, 
                      jump=0.01, wvar0=1, updatecov=50, ntrydr= 2,
                      burninlength=1000
                      )
              )
      )

MCMC$pars <- exp(MCMC$pars)

save(MCMC, file = "output/05_MCMC_single.RData")
write.csv(MCMC$pars,           
          file = "tables/05_MCMC_single_pars.csv", 
          row.names = TRUE)

png("figs/05_MCMC_single_chain.png", 
    width = 6, height = 6, units = 'in', res = 300)
  plot(MCMC, Full=TRUE)
dev.off()

png("figs/05_MCMC_single_pair.png", 
    width = 6, height = 6, units = 'in', res = 300)
  pairs(MCMC)
dev.off()
  
MCMC$count

summary(MCMC)
write.csv(summary(MCMC), 
          file = "tables/05_MCMC_single_stat.csv", 
          row.names = TRUE)

cov(MCMC$pars)

summary(Fit)$cov.scaled 

cor(MCMC$pars)

exp(MCMC$bestpar)

# Save calibrated parameter set
input_param_3  <- p
for (i in 1:length(exp(MCMC$bestpar))){
  nval = names(exp(MCMC$bestpar[i]))
  input_param_3[nval] = as.numeric(exp(MCMC$bestpar[i]))
}
save(input_param_3,file = "data/input_param_label_1_bestpar.RData")
write.csv(input_param_3, "data/input_label_1_bestpar.csv", 
          quote=FALSE, row.names=FALSE)

# Monte Carlo Run
SF <- function (pars) {
   out <- PCPF1R(pars, parms2 = p6, water=water, DMAX=21,type=2, fdes=1)
   return(out)
   }
Sens2 <- sensRange(func=SF, parInput=MCMC$par, sensvar="Cpw")

save(Sens2, file="output/05_MCMC_MCS.RData")
write.csv(Sens2, "output/05_MCMC_MCS.csv", quote=FALSE, row.names=FALSE)

# Visual check
png("figs/05_MCMC_MCS_linear.png", 
    width = 6, height = 6, units = 'in', res = 300)
  plot(summary(Sens2), xlim=c(0,21), ylim=c(0, 1), ylab = "Concentration (mg/L)", quant=TRUE,
       main=paste(p$name,": Uncertainty analysis at ",p$plot), xlab="Day after application",
       cex.lab=1.2, legpos="topright")
  for (i in 1:(nrow(obs))) {
    if (obs[i,2]=="="){
      points(obs$DAHA[i], obs$CONC.[i], pch=1, cex=2.5, col = "red")
    } else if(obs[i,2]=="<") {
      points(obs$DAHA[i], obs$CONC.[i], pch=19, cex=2.5, col = "red")
    }
  }
dev.off()

png("figs/05_MCMC_MCS_log.png", 
    width = 6, height = 6, units = 'in', res = 300)
  plot(summary(Sens2), xlim=c(0,21), ylim=c(0.001, 1), ylab = "Concentration (mg/L)", quant=TRUE,
       main=paste(p$name,": Uncertainty analysis at ",p$plot), xlab="Day after application",
       cex.lab=1.2,legpos="topright", log="y")
  for (i in 1:(nrow(obs))) {
    if (obs[i,2]=="="){
      points(obs$DAHA[i], obs$CONC.[i], pch=1, cex=2.5, col = "red")
    } else if(obs[i,2]=="<") {
      points(obs$DAHA[i], obs$CONC.[i], pch=19, cex=2.5, col = "red")
    }
  }
dev.off()


# Run with bestpar
# Select parameter set
out3 <- PCPF1R(exp(MCMC$bestpar), p6, water=water,DMAX=21,fdes=1,type=2)
save(out3, file = "output/05_MCMC_output.RData")
write.csv(out3, "output/05_MCMC_output.csv", quote=FALSE, row.names=FALSE)

# Goodness of fitting for cold simulation
Y      <-  d[1]
Z1     <-  c("Time","Cpw")
out3d  <-  XXL(out3, Y, Z1)
stat_3 <-  gof(sim=out3d$Cpw, obs=d$Cpw)
stat_3
save(stat_3, file = "output/05_stat_MCMC.RData")
stat_F <-  as.data.frame(cbind(stat_1,stat_2,stat_3))[c("NSE","rNSE","bR2","PBIAS %","RSR"),]
colnames(stat_F)  <- c("Cold run","Model fitting","MCMC")
write.csv(stat_F,           
          file = "tables/05_MCMC_stat_F.csv", 
          row.names = TRUE)

# Visual checks for both linear and log scales
png("figs/05_MCMC_conc_linear.png", 
    width = 6, height = 6, units = 'in', res = 300)
  plot(out2$Time, out2$Cpw, xlim=c(0,21), ylim=c(0,1), lty=1,lwd = 2, type="l",
       main=paste(p$name,": MCMC-calibrated simulation at ",p$plot), ylab ="Concentration (mg/L)", 
       xlab = "Day after application (day)",cex.lab=1.2)
  for (i in 1:(nrow(obs))) {
    if (obs[i,2]=="="){
      points(obs$DAHA[i], obs$CONC.[i], pch=1, cex=2.5, col = "red")
    } else if(obs[i,2]=="<") {
      points(obs$DAHA[i], obs$CONC.[i], pch=19, cex=2.5, col = "red")
    }
  }
  legend("topright", c("measured", "simulated"),lty = c(NA, 1), 
         pch = c(1, NA), cex=1.2,bty="n", col=c("red", "black"))
dev.off()

png("figs/05_MCMC_conc_log.png", 
    width = 6, height = 6, units = 'in', res = 300)
  plot(0,0.001, type = "n", bty = "n", xlim=c(0,21), ylim=c(0.001,1),
       yaxt="n", xaxt = "n", ylab = "Concentration (mg/L)", 
       xlab="Day after application (day)",log="y",cex.lab=1.2,
       main=paste(p$name,": MCMC-calibrated simulation at ",p$plot))
  axis(1, at=seq(0,21,3),cex.axis=1.1)
  axis(2, at=c(0.001, 0.01 ,0.1,1), 
       labels=c("0.001","0.01", "0.1","1"),las=1, cex.axis=1.2)
  at.y <- outer(1:9, 10^(-3:0))
  lab.y <- ifelse(log10(at.y) %% 1 == 0, at.y, NA)
  axis(2, at=at.y, labels=lab.y, tcl=par("tcl")*0.5, las=1, cex.axis=1.2)
  lines(out2$Time, out2$Cpw, lty=1,lwd = 2)
  box()
  for (i in 1:(nrow(obs))) {
    if (obs[i,2]=="="){
      points(obs$DAHA[i], obs$CONC.[i], pch=1, cex=2.5, col = "red")
    } else if(obs[i,2]=="<") {
      points(obs$DAHA[i], obs$CONC.[i], pch=19, cex=2.5, col = "red")
    }
  }
  legend("topright", c("measured", "simulated"),lty = c(NA, 1), 
         pch = c(1, NA), cex=1.2,bty="n", col=c("red", "black"))
dev.off()


```

```{r }


# Advanced application: MCMC with multiple chains
iniPar <- data.frame(Chain1=exp(coef(Fit)), Chain2=exp(coef(Fit)), Chain3=exp(coef(Fit)))
iniPar <- sweep(iniPar, MARGIN = 2, STATS = c(1, 0.9, 1.1), FUN = "*")
var0 <- Fit$var_ms_unweighted
cov0 <- summary(Fit)$cov.scaled * 2.4 ^ 2/5

# Reset parameter range
ppl <- 0.9*pmax((0.5*exp(coef(Fit))),exp(ppl))
ppu <- 1.1*pmin((2*exp(coef(Fit))),exp(ppu))
ppl <- log(ppl)
ppu <- log(ppu)

print(system.time(
                  MCMC <- apply(iniPar, MARGIN = 2, FUN = function(iIniPar) {
                                  modMCMC(f=F, p=log(iIniPar), niter=5000, lower=ppl, upper=1.1*ppu, 
                                          jump = cov0, var0 = var0, wvar0 = 1, updatecov = 50,#ntrydr=2,
                                          burninlength=0, outputlength=5000)
                     })
                    )
      )

# Check the convergence of chains
MC <- as.mcmc.list(lapply(MCMC2, FUN = function(x) {
                   mcmc(as.matrix(exp(x$pars)))#,start=1, end=1000, thin=1))
                   }))

# Visual assessment using ggmcmc package
if (!require("ggmcmc")) install.packages("ggmcmc")
library(ggmcmc) 
parDRAM <- ggs(MC)
#burnParDRAM <- filter(parDRAM, Iteration > 500)

ggs_traceplot(parDRAM)

ggs_density(parDRAM)

ggs_pairs(parDRAM, lower = list(continuous = "density"))

# Statistical assessment
gelman.diag(MC,autoburnin = FALSE)
autocorr.diag(MC)
geweke.diag(MC)

# Statistical summary of MCMC
summary(MC)

# Best parameter set
lapply(MCMC, FUN = function(x) {as.data.frame(exp(x$bestpar))})
Bestparam <- lapply(MCMC, FUN = function(x) {as.data.frame(exp(x$bestpar))})

# Posterior covariance
lapply(MCMC, FUN = function(x) {cov(as.matrix(exp(x$par)))})

```

```{r }
# STEP 6: Application
```

```{r }
# Read PCPF-BR model and sub-function
source("R/PCPF-BR.R")
source("R/WBcalc.R")

meteo    <- read.csv("data-raw/data_meteodef.csv",header=T)
flow     <- read.csv("data-raw/data_flowdef.csv",header=T)
pcpfin   <- read.csv("data/input_label_1_bestpar.csv",header=T)
waterin  <- read.csv("data-raw/input_wbcalc.csv",header=T)
blockin  <- read.csv("data-raw/input_blockcalc.csv",header=T)

# Cold run
outB1    <- PCPFBR(pcpfin, waterin, blockin, flow, meteo, DMAX=30, type=2)
save(out3, file = "output/06_prediction_coldrun.RData")
write.csv(out3, "output/06_prediction_coldrun.csv", quote=FALSE, row.names=FALSE)

png("figs/06_prediction_coldrun.png", 
    width = 8, height = 6, units = 'in', res = 300)
  par(mar = c(4, 4, 4, 4))
  plot(outB1$DASS,outB1$PEC,xlab="Day After Simulation Started",ylab="Conc. [ppb]",
       ylim=c(0,1),type="l",lwd=2, las=2)
  par(new=T)
  barplot(outB1$AppAmount/1000, ylim=c(50,0),yaxt="n")
  axis(4, at=c(50,40,30,20,10,0), labels=c("50","40","30","20","10","0"), las=2)
  corners = par("usr") #Gets the four corners of plot area (x1, x2, y1, y2)
  par(xpd = TRUE) #Draw outside plot area
  text(x = corners[2]+3, y = mean(corners[3:4]), "App.amount [kg]", srt = 270)
dev.off()

# Create MCS parameter set
# For block calculation parameters
pars_B   <-  c(Hmax     =  5, 
               ddrain   =  0.5, 
               dperc    =  0.5, 
               dseep    =  0.1, 
               WHP      =  1,
               hflow    =  3,
               pfr      =  0.05,
               usage    =  0.1,
               Klevee   =  17.22,
               AppStdev =  1
               )
parRanges <- data.frame(min = c( 1,  0.1, 0.1,  0.1,  0,   1,  0.01, 0.05, 10, 1), 
                        max = c(10,  1.0,  1,   1.0,  7,  10,  0.2,  0.3,  25, 5)
                        )
rownames(parRanges)<- c("Hmax", "ddrain", "dperc", "dseep", "WHP", "hflow", 
                        "pfr", "usage", "Klevee","AppStdev")
parRanges
parlist_B <- Latinhyper(parRanges, 500)

# Retrieving PCPF inputs from posterior distributions 
load("output/05_MCMC_single.RData")
pars_P  <- exp(MCMC$bestpar)
POSTERI <- function (pars) {
  out <- pars
  return(out)
}
parlist_P <- sensRange(func=POSTERI, parInput=MCMC$par, num=500)[names(pars_P)]

# Build final parameter set for MCS
pars     <- c(pars_B, pars_P)
parlist  <- cbind(parlist_B,parlist_P)

# Monte Carlo run
MP       <- 30
SFB <- function (pars) {
   X <- pcpfin
   Y <- waterin
   Z <- blockin
   for (i in 1:length(pars)){
     nval <- names(pars[i])
     if (nval %in% names(X)){
       X[nval] = as.numeric(pars[i])
     } else if (nval %in% names(Y)){
       Y[nval] = as.numeric(pars[i])
     } else if (nval %in% names(Z)){
       Z[nval] = as.numeric(pars[i])
     }    
   }
   out <- PCPFBR(pcpfin=X, waterin=Y, blockin=Z, flow, meteo, DMAX=MP, type=2)
   return(out)
}

SensB     <- sensRange(func=SFB,parms=pars,sensvar="PEC",parInput=parlist,num=500)
save(SensB, file="output/06_prediction_MCS.RData")
write.csv(SensB, "output/06_prediction_MCS.csv", quote=FALSE, row.names=FALSE)
summary_SensB <- summary(SensB) 
save(Sens2, file="output/06_prediction_summary_MCS.RData")
write.csv(Sens2, "output/06_prediction_summary_MCS.csv", quote=FALSE, row.names=FALSE)

png("figs/06_prediction_MCS.png", 
    width = 8, height = 6, units = 'in', res = 300)
  plot(summary(SensB), xlim=c(0,30), legpos="topright", quant=TRUE,
       main="",cex.lab=1.2, xlab="Day After Simulation Started", ylab=expression(paste("Conc [", mu,"g/L]")))
dev.off()

# Analyze simulated data
# Calculate SRRC
SensB2          <- SensB
SensB2$PECMAX   <- apply(SensB2[,(length(pars)+1):(length(pars)+MP)],1,max)
save(SensB2, file="output/06_prediction_MCS_2.RData")
write.csv(SensB2, "output/06_prediction_MCS_2.csv", quote=FALSE, row.names=FALSE)
X               <- SensB2[,1:length(pars)]
y               <- as.vector(SensB2[,"PECMAX"])
SRRCB           <- src(X, y, rank = TRUE)
print(SRRCB)
SRRC_table2     <- data.frame(parameter=row.names(SRRCB$SRRC),SRRCB$SRRC)
write.csv(SRRC_table2, 
          file = "tables/06_prediction_block_SRRC.csv", 
          row.names = FALSE)
SRRC_table2s     <- SRRC_table2[order(abs(SRRC_table2[,2])),]
SRRC_table2s_nam <- SRRC_table2s[(nrow(SRRC_table2s)-4):nrow(SRRC_table2s),1]
png("figs/06_prediction_block_SRRC.png", 
    width = 8, height = 6, units = 'in', res = 300)
  par(mar = c(2, 5, 2, 2))
  barplot(SRRC_table2s[,2],names.arg=SRRC_table2s[,1],horiz=T,xlim=c(-1,1),las=1)
  box()
dev.off()


# Endpoint (3ug/L) assessment
EP              <- 3
png("figs/06_prediction_block_hist.png", 
    width = 6, height = 6, units = 'in', res = 300)
  hist(SensB2$PECMAX,breaks="FD",xlim=c(0,20))
  abline(v=EP)
  box()
dev.off()
SensB3          <- SensB2[SensB2$PECMAX>EP,]
save(SensB3, file="output/06_prediction_MCS_3.RData")
write.csv(SensB3, "output/06_prediction_MCS_3.csv", quote=FALSE, row.names=FALSE)
summary_SensB3  <- apply(SensB3[,1:(length(pars))],2,summary)
summary_SensB3
write.csv(summary_SensB3,           
          file = "tables/06_prediction_summary_MCS.csv", 
          row.names = TRUE)

png("figs/06_prediction_block_boxplot.png", 
    width = 8, height = 3, units = 'in', res = 300)
par(mfrow = c(1, 5))
for (i in 1:5) {
  BP <- SRRC_table2s_nam[5-i+1]
  boxplot(SensB3[,BP])
  abline(h=c(pcpfin, waterin, blockin)[BP], col="red")
  axis(1, at=1, labels = BP, cex.axis = 1.5)
}
dev.off()
```
